The Socialization of Meritocracy: The role of the Family and the School

### 2023-06-07 paper-blinded.Rmd

coef_names <- c(
  "Sense of Justice in grades - Indirect (ln)",
  "Less than I deserve",
  "More than I deserve ",
  "Hard work is important¹",
  "Quintile 2","Quintile 3","Quintile 4","Quintile 5","Quintile Don't know/No Answer",
  "Parents have universitary degree (ref: does not have)",
  "School Socio-economic status",
  "Hard work is important x Less than I deserve",
  "Hard work is important x More than I deserve"
  ) # Nombre coeficientes

@@

# Renderizar tabla
knitreg(list(getah.or0.1,getah.or0.2,getah.or0.3,
             # getah.or1,
             getah.or6,
             # getah.or7,
             getah.or8),
        caption = paste("(\\#tab:getah)",cap1),
        caption.above=TRUE,
        omit.coef=omit_coef,
        include.thresholds=FALSE,
        custom.gof.rows=list(Controls=c("No","No","No",
                                        # "No",
                                        # "Yes",
                                        "Yes","Yes")),
        groups=list("Sense of Justice in grades - Direct (ref: The ones I deserve)"=2:3,
                    "Parental Perc. Meritocracy (ref: Not important)"=4,
                    "Household income (ref: Quintile 1)"=5:9,
                    "Interaction: Parental Perc. Meritocracy x SJ in grades - Direct" = 12:13),
        custom.coef.names=coef_names,
        scalebox = 0.75,
        threeparttable = T,
        custom.note="\\item *** p < 0.001; ** p < 0.01; * p < 0.05; \\item ¹Note: the perception of parent’s meritocracy was collapsed into dummies, where the category 'It is important' (1) includes the categories 'Very important', 'Important' and 'Somewhat important' and the reference category 'Not important' (0) corresponds to the category 'Not at all important'."
        #file = "output/tables/trabajoduro_ppt.html"
        )
#webshot::webshot("output/tables/trabajoduro_ppt.html","output/tables/trabajoduro_ppt.png")
```

@@

>>>>

 # Nombre coeficientes

coef_names <- c(
  "Sense of Justice in grades - Indirect (ln)",
  "Less than I deserve",
  "More than I deserve ",
  "Hard work is important¹",
  "Quintile 2",
  "Quintile 3",
  "Quintile 4",
  "Quintile 5",
  "Quintile Don't know/No Answer",
  "Parents have universitary degree (ref: does not have)",
  "School Socio-economic status",
  "Hard work is important x Less than I deserve",
  "Hard work is important x More than I deserve"
  ) # Nombre coeficientes

@@

# Renderizar tabla
htmlreg(list(getah.or0.1,getah.or0.2,getah.or0.3,
             # getah.or1,
             getah.or6,
             # getah.or7,
             getah.or8),
        caption = paste("(\\#tab:getah)",cap1),
        caption.above=TRUE,
        omit.coef=omit_coef,
        include.thresholds=FALSE,
        custom.gof.rows=list(Controls=c("No","No","No",
                                        # "No",
                                        # "Yes",
                                        "Yes","Yes")),
        groups=list("Sense of Justice in grades - Direct (ref: The ones I deserve)"=2:3,
                    "Parental Perc. Meritocracy (ref: Not important)"=4,
                    "Household income (ref: Quintile 1)"=5:9,
                    "Interaction: Parental Perc. Meritocracy x SJ in grades - Direct" = 12:13),
        custom.coef.names=coef_names,
        scalebox = 0.75,
        threeparttable = T,
        custom.note="\\item *** p < 0.001; ** p < 0.01; * p < 0.05; \\item ¹Note: the perception of parent’s meritocracy was collapsed into dummies, where the category 'It is important' (1) includes the categories 'Very important', 'Important' and 'Somewhat important' and the reference category 'Not important' (0) corresponds to the category 'Not at all important'.",
        file = "output/tables/trabajoduro_ppt.xls"
        )
#webshot::webshot("output/tables/trabajoduro_ppt.html","output/tables/trabajoduro_ppt.png")

```{r plotgetah, eval=FALSE, include=FALSE}
# Funciones para renderizar tablas tanto en HTML como en pdf
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, haven, texreg, sjPlot, lme4, ordinal, webshot) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias
                      cache = FALSE,    # cache de los chunks,usar analisis pesados
                      out.width = '85%',# largo de imagen en %
                      fig.pos= "H",     # posicion figuras H = HERE
                      echo = FALSE      # incluir chunk en output
                      )

getah.or6 <- ordinal::clmm(formula(paste("perc_trabajo_duro_factor_est~",paste(c("perc_tduro_bi_ap","sj_indirect_ln","sj_direct_factor",con,ref),collapse="+"))), basereg, nAGQ = 10)

getah.or8 <- ordinal::clmm(formula(paste("perc_trabajo_duro_factor_est~",paste(c("perc_tduro_bi_ap","sj_indirect_ln","sj_direct_factor", con, "perc_tduro_bi_ap*sj_direct_factor","nse_grupo",ref),collapse="+"))), basereg)

rm_plot <- c(
  "Not important|Somewhat important",
  "Somewhat important|Important",
  "Important|Very important",
  "quintiles_ingresos_pc_factorDon't know/No response",
  "libros_hogar_factor_apBetween 11 and 25 books",
  "libros_hogar_factor_apBetween 26 and 100 book",
  "libros_hogar_factor_apBetween 101 and 200 books",
  "libros_hogar_factor_apBetween 201 and 500 books",
  "libros_hogar_factor_apMore than 500 books",
  # "univ",
  "pos_pol_factor_apCenter Right",
  "pos_pol_factor_apCenter",
  "pos_pol_factor_apCenter Left",
  "pos_pol_factor_apLeft",
  "pos_pol_factor_apIndependent",
  "pos_pol_factor_apNone",
  "pos_pol_factor_apNa/Nr",
  "pos_pol_factor_estCenter Right",
  "pos_pol_factor_estCenter",
  "pos_pol_factor_estCenter Left",
  "pos_pol_factor_estLeft",
  "pos_pol_factor_estIndependent",
  "pos_pol_factor_estNone",
  "pos_pol_factor_estNa/Nr",
  "genero_factor_estMujer",
  "genero_factor_estOtro",
  "dependencia_factor_apPart. Subvencionado",
  "dependencia_factor_apPart. Privado")

coef_names <- c(
    "Hard work is important (ref: Not important)",
  "Sense of Justice in grades - Indirect (ln)",
  "Less than I deserve (ref: The ones I deserve)",
  "More than I deserve ",
  "Quintile 2 (ref: Quintile 1)",
  "Quintile 3",
  "Quintile 4",
  "Quintile 5",
  # "Quintile Don't know/No Answer",
  "Parents have universitary degree (ref: does not have)",
  "School Socio-economic status",
  "Hard work is important x Less than I deserve",
  "Hard work is important x More than I deserve"
  ) # Nombre coeficientes

library(pBrackets)
library(grid)

# plotgetah<- 
# plot_model(getah.or8,rm.terms = rm_plot,show.intercept = F,
#            show.p = T, show.values = T,
#            # order.terms = c(2,3,4,1,5,6,7,8,9,10,11,12),
#            axis.labels = rev(coef_names),
#            ) +
#   geom_hline(yintercept = 1)
# plotgetah
plotgetah<- 
plot_models(getah.or6,getah.or8,rm.terms = rm_plot,
            axis.labels = rev(coef_names),show.values = T,
            m.labels = c("Individual", "Interactions"),
            legend.title = "Models") +
  geom_hline(yintercept = 1) +
  theme(legend.position = "bottom")

ggplot2::ggsave(plot = plotgetah,device = "png",units = "cm",
                width = 1,height = 1,scale = 18,
                path =  "presentacion-effort/images/",
                filename = "plotgetahead.png")
# Elaborar modelo de interacción
getah.or7 <- ordinal::clmm(formula(paste("perc_trabajo_duro_factor_est~",paste(c("perc_tduro_bi_ap","sj_indirect_noln","sj_direct_factor", con, "perc_tduro_bi_ap*sj_direct_factor",ref),collapse="+"))), basereg)

graph_interact

ggplot2::ggsave(plot = graph_interact,device = "png",units = "cm",
                width = 1,height = 1,scale = 18,
                path =  "presentacion-effort/images/",
                filename = "intergetahead.png")
```

@@

```{r ploteffort, eval=FALSE, include=FALSE}
# Funciones para renderizar tablas tanto en HTML como en pdf
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, haven, texreg, sjPlot, ggplot2, ordinal, webshot) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias
                      cache = FALSE,    # cache de los chunks,usar analisis pesados
                      out.width = '85%',# largo de imagen en %
                      fig.pos= "H",     # posicion figuras H = HERE
                      echo = FALSE      # incluir chunk en output
                      )

effort.or6 <- ordinal::clmm(formula(paste("perc_esfuerzo_factor_est~",paste(c("perc_esfuerzo_bi_ap","sj_indirect_ln","sj_direct_factor", con,ref),collapse="+"))), basereg)
effort.or8 <- ordinal::clmm(formula(paste("perc_esfuerzo_factor_est~",paste(c("perc_esfuerzo_bi_ap","sj_indirect_ln","sj_direct_factor", con, "perc_esfuerzo_bi_ap*sj_direct_factor","nse_grupo",ref),collapse="+"))), basereg)

rm_plot <- c(
  "Strongly Disagree|Disagree",
  "Disagree|Agree",
  "Agree|Strongly Agree",
  "quintiles_ingresos_pc_factorDon't know/No response",
  "libros_hogar_factor_apBetween 11 and 25 books",
  "libros_hogar_factor_apBetween 26 and 100 book",
  "libros_hogar_factor_apBetween 101 and 200 books",
  "libros_hogar_factor_apBetween 201 and 500 books",
  "libros_hogar_factor_apMore than 500 books",
  # "univ",
  "pos_pol_factor_apCenter Right",
  "pos_pol_factor_apCenter",
  "pos_pol_factor_apCenter Left",
  "pos_pol_factor_apLeft",
  "pos_pol_factor_apIndependent",
  "pos_pol_factor_apNone",
  "pos_pol_factor_apNa/Nr",
  "pos_pol_factor_estCenter Right",
  "pos_pol_factor_estCenter",
  "pos_pol_factor_estCenter Left",
  "pos_pol_factor_estLeft",
  "pos_pol_factor_estIndependent",
  "pos_pol_factor_estNone",
  "pos_pol_factor_estNa/Nr",
  "genero_factor_estMujer",
  "genero_factor_estOtro",
  "dependencia_factor_apPart. Subvencionado",
  "dependencia_factor_apPart. Privado")

coef_names <- c(
  "Effort is rewarded (ref: Effort is not rewarded)",
  "Sense of Justice in grades - Indirect (ln)",
  "Less than I deserve (ref: The ones I deserve)",
  "More than I deserve",
  "Quintile 2 (ref: Quintile 1)",
  "Quintile 3",
  "Quintile 4",
  "Quintile 5",
  # "Quintile Don't know/No Answer",
  "Parents have universitary degree (ref: does not have)",
  "School Socio-economic status",
  "Effort is rewarded x Less than I deserve",
  "Effort is rewarded x More than I deserve"
  ) # Nombre coeficientes

library(pBrackets)
library(grid)

# ploteffort<- 
# plot_model(effort.or8,rm.terms = rm_plot,show.intercept = F,
#            show.p = T, show.values = T,
#            order.terms = c(2,3,4,1,5,6,7,8,9,10,11,12),
#            axis.labels = rev(coef_names),
#            ) +
#   geom_hline(yintercept = 1)
# ploteffort

ploteffort<- 
plot_models(effort.or6,effort.or8,rm.terms = rm_plot,
            axis.labels = rev(coef_names),show.values = T,
            m.labels = c("Individual", "Interactions"),
            legend.title = "Models") +
  geom_hline(yintercept = 1) +
  theme(legend.position = "bottom")

ggplot2::ggsave(plot = ploteffort,device = "png",units = "cm",
                width = 1,height = 1,scale = 19,
                path =  "presentacion-effort/images/",
                filename = "ploteffort.png")
# Elaborar modelo de interacción
effort.or7 <- ordinal::clmm(formula(paste("perc_esfuerzo_factor_est~",paste(c("perc_esfuerzo_bi_ap","sj_indirect_ln","sj_direct_factor", con, "perc_esfuerzo_bi_ap*sj_direct_factor",ref),collapse="+"))), basereg)

graph_interact

ggplot2::ggsave(plot = graph_interact,device = "png",units = "cm",
                width = 1,height = 1,scale = 18,
                path =  "presentacion-effort/images/",
                filename = "intereffort.png")
```
